---
output:
  pdf_document: default
  html_document: default
---
**AB Test of eCommerce website**

- There were 298,234 visiting times of the website last week. The server showed A and B versions with equal times among all the visits.

- There were 8365 successful conversions in version A, and 8604 successful conversions in version B.

Do A and B versions of the website give the website the same conversion rate? What is the significance level?

```{r}
visits.per.group <- 298234/2
success.A <- 8365
success.B <- 8604
conversion.rate.A <- success.A / visits.per.group
conversion.rate.B <- success.B / visits.per.group
```

Perform a proportional hypothesis test

- H0 (null hypothesis): conversion rates of version A and B are the same.
- H1 (alternative hypothesis): conversion rates of version A and B are different.
```{r}
proportion.test.results <- prop.test(x=c(success.A, success.B), n=c(visits.per.group, visits.per.group),
                                     alternative="two.sided",
                                     conf.level=0.95, correct=TRUE)
proportion.test.results 
```
What is the possibility that we accept  H0  when  H1  is true?
```{r}
proportion.test.power <- power.prop.test(n=visits.per.group, p1=conversion.rate.A, p2=conversion.rate.B, sig.level=0.05)
print(proportion.test.power)
```

